RD design analysis

### 2024-01-05 analysis/RD design analysis.Rmd
Add files via upload

```{r}
control_variables <- c(
  "jiadian", "kind", "hotel", "shop_mall", "museum", "old", "ktv", "mid", "prim", "west_food", "super", "sub", "park", 
  "area", "bedroom", "toilet", "house_age", "floor_level", "green_ratio", "total_building", "total_floor_number", "living_room", "elevator_ratio", "kitchen", "floor_ratio", "total_resident",
  "pm25", "pop", "light",
  "non_online_effect", "ln_negotiation_period", "ln_watch_time", "ln_nego_changes", "ln_lead", "ln_watch_people"
)
```

@@

Conducting placebo test

```{r}
# using the same bandwidth
unrelated_result <- rdrobust(y = panel_data$ln_negotiation_period, 
                             x = panel_data$nearest_store_distances, c = 0.41, h = 0.066, b = 0.135)
print("Placebo test with unrelated outcome:")
print(unrelated_result)
pander(cbind(unrelated_result$coef, unrelated_result$pv))
```

>>>>

```{r}
control_variables <- c(
  "jiadian", "kind", "hotel", "shop_mall", "museum", "old", "ktv", "mid", "prim", "west_food", "super", "sub", "park", 
  "area", "bedroom", "toilet", "house_age", "floor_level", "green_ratio", "total_building", "total_floor_number", "living_room", "elevator_ratio", "kitchen", "floor_ratio", "total_resident",
  "pm25", "pop", "light",
  "non_online_effect", "ln_negotiation_period", "ln_watch_time", "ln_nego_changes", "ln_lead", "ln_watch_people"
)
testing_variables <- c("ln_negotiation_period", "ln_watch_time", "ln_nego_changes", "ln_lead", "ln_watch_people", "ln_end_price")
```

@@

Conducting placebo test. We shall using the same validation bandwidth and bias correction bandwidth. The results are good overall

```{r}
for (validation in testing_variables) {
  rd_result <- rdrobust(y = panel_data[[validation]], x = panel_data$nearest_store_distances
                        , c = 0.41, h = 0.066, b = 0.135)
  cat("Covariate:", validation, "\n")
  print(summary(rd_result))
  cat("\n\n")

}
```
